---
title: "Reconstitution Code"
author: "Marshall"
date: "2024-06-12"
output: html_document
---

```{r dependecies}
#| include: true
#| warning: false
#| message: false
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(readxl)# For importing from excel spreadsheets
library(visNetwork)#networking interactive graph package
library(lubridate)

```

##This code will automatically accept either 1 or 2 datasets as an input and doesn't care which order you put them in as long as the empty one is coded as NULL


```{r import and initial cleaning, include=FALSE}

load_data<-function(data_set_1, data_set_2) {
  if(is.null(data_set_1)==FALSE & is.null(data_set_2)==FALSE){
    rbind(data_set_1,data_set_2)#this is when both datasets have information in them
    }
  if(is.null(data_set_1)==FALSE){
  raw_data<-read_excel(data_set_1)#this section is if data set 1 contains the information
  }
  else{
    raw_data<-read_excel(data_set_2)#this section is if data set 2 contains the information
  }
  raw_data <-raw_data%>%
  rename(id="Addresskey",
         List="List Year",
         Effective="Effective Date",
         Alteration="List Alteration Date",
         Assessment="Ass Ref",
         Case="Case Number",
         change_reason="Change Reason")
raw_data%>%
  mutate(Effective=if_else(is.na(Effective), as.Date("1995/04/01"), Effective))%>%
    mutate(effective_date=str_replace_all(Effective,"-","/"))#formatting the dates to be better
} 
raw_data<-load_data("Data/Mortgage broker case.xlsx",NULL)
raw_data<-load_data("C:/Users/thoma/OneDrive/Documents/Goodman Nash/Business-Rates/Data/Part 2 AK11002881000.xlsx","C:/Users/thoma/OneDrive/Documents/Goodman Nash/Business-Rates/Data/Part 1 AK11002881000.xlsx")
```

##the following function creas the node data

```{r creating the node data, echo=TRUE}

nodes_creation<-function(node_input){
node_input%>%
  select(id,effective_date,RV)|>#creating the nodes list
  group_by(id)|>
  slice(which.max(as_date(effective_date)))|>#selecting the RV based on the most recent entry for each id
  ungroup()%>%
    mutate(RV=if_else(is.na(RV), -1, RV))|>
  mutate(group=case_when(RV>0&RV<2900~"Below Threshold",
                       RV>=12000&RV<15000~"Partial SBR",
                       RV==0~"Zero",
                       RV>=2900&RV<12000~"Full SBR",
                       RV<0~"Old",
                       RV>=15000~"Inelligible"))
}
nodes<-nodes_creation(raw_data)
```
##creating the edge data for the reconstitution data

```{r creating the edge data for reconstitutions data, echo=TRUE}
reconstitution_edge_creation<-function(reconstitution_data){
  cases<-reconstitution_data%>%
  group_by(Case)%>%
  group_by(Relationship)|>#creating a new data set that is grouped for checking purposes
    mutate(from=0, to=0)|>
    mutate(to=ifelse(Relationship=="Child",
                     id, to))|>#for child cases putting the AK in the to column 
    mutate(from=ifelse(Relationship=="Parent",
                       id, from))#for parent cases putting the AK in the from column
  
parent_values <- cases%>%
  filter(Relationship=="Parent")%>%
  select(id,Case,Relationship)#creating the parent data

child_values <- cases%>%
  filter(Relationship=="Child")%>%
  select(id,Case,Relationship)#creating the child data

final_cases<-left_join(cases,parent_values,by="Case",relationship = "many-to-many")|>#binds the parent data to the cases dataset
  rename(id="id.x",Relationship="Relationship.x")

final_cases<-final_cases%>%
  group_by(Case)%>%
  mutate(colours=ifelse(Relationship=="Parent",1,ifelse(Relationship=="Child",2,NA)))|>
  mutate(color=ifelse(sum(colours==1,na.rm=TRUE)>sum(colours==2,na.rm=TRUE)/2,
                             "grey","pink"))

final_cases<-final_cases%>%
  ungroup(Case)%>%
  filter(Relationship!=is.na(final_cases$Relationship))%>%
  mutate(from=ifelse(Relationship=="Child"&from==0&to!=0,
                   id.y,from))#creating the matching algorithm for cases to create the from and to column

link_data<-data.frame(final_cases$from,final_cases$to,final_cases$color)|>
  rename(from="final_cases.from",to="final_cases.to",color="final_cases.color")|>#the reconstitution data frame
  filter(from!=0)%>%
  filter(to!=0)%>%#removing any values that are 0
  distinct()#removing any duplicates
}
reconstitution_edge<-reconstitution_edge_creation(raw_data)
```
##creating the edge data for the address change data

```{r creating the edge address change edge data, echo=TRUE}
address_edge_creation<-function(address_data){
  address_change_data<-address_data%>%
  filter(change_reason=="ADDRESS CHANGE & REVIEW OF ASSESSMENT")|>
    mutate(RV=if_else(is.na(RV), 0, RV))|>#creating the data set for address changes
  mutate(from=if_else(RV==0,id,0),
         to=if_else(RV!=0,id,0))
  #matching the data set to create the columns
address_from_data<-address_change_data%>%
  sort_by(address_change_data$Case)%>%
  filter(from!=0)#ordering the data so that the resulting data frame matches correctly and then filtering out the irrelevant data for one half of the data set
address_to_data<-address_change_data%>%
  sort_by(address_change_data$Case)%>%
  filter(to!=0)

#ordering the data so that the resulting data frame matches correctly and then filtering out the irrelevant data for one half of the data set

address_link_data<-data.frame(address_from_data$from,address_to_data$to)%>%
  rename(from="address_from_data.from",
         to="address_to_data.to")|>#creating this data set
  distinct()|>#removing any duplicates
  mutate(color="purple")#adding this column so the edges colour correctly in the graph
}
address_edge<-address_edge_creation(raw_data)
```
##creating the graph itself. First it links the edge and node datasets together and then creates the label for the plot itself before creating the plot


```{r creating the plots, echo=TRUE}

create_graph<-function(nodes,address,reconstitution){
link_data_all<-rbind(address,reconstitution)#joining the 2 sets of edge data together

ledges<-data.frame(color=c("pink","purple","grey"),
                   label=c("Split","ADDRESS CHANGE & REVIEW OF ASSESSMENT","Merge"),
                   width=5)#label for the graph

network_graph<-visNetwork(nodes,link_data_all,width="100%")%>%
  visNodes(physics=FALSE)%>%
  visEdges(arrows = "middle",width = 5)%>%
  visGroups(groupname = "Zero", color="lightblue")%>%
  visGroups(groupname = "Below Threshold", color="lightgreen")%>%
  visGroups(groupname = "Partial SBR", color="orange")%>%
  visGroups(groupname = "Inelligible", color="red")%>%
  visGroups(groupname = "Full SBR", color="darkgreen")%>%
  visGroups(groupname = "Old", color="brown")%>%
  visOptions(nodesIdSelection = TRUE,highlightNearest = TRUE,selectedBy = "group")%>%
  visLegend(addEdges = ledges,
            addNodes=list(font.color = "white"))
}
graph<-create_graph(nodes,address_edge,reconstitution_edge)
visSave(graph,"Interactive graph.html")#saves the graph

```

### Address Key Hyperlink Function
Function for creating address keys:
```{r include=FALSE}
library(stringr)

create_address_key_link <- function(address_key) {
    str_glue("<a href=\"http://gnsql/gmn/QueryViewerBeta/VOAQueryV3.aspx?AddKey={address_key}\">{address_key}</a>")
}
```


